title

### 2013-02-04 paper.tex
small changes

In light of the 2012-2013 drought season, and the possibility of potentially
more severe droughts in the future, our department has conducted an
analysis of how best to satisfy the water needs of the United States.

The first part of our analysis is a projection of future water needs. 
We used data from previous years to predict the amount of additional
water that each county will need by 2025. Creating such a projection is critical, as it informs us
of what kinds of infrastructure needs to be developed, and how significant of a problem water shortages are likely to be in the future.

Our projections suggest that water shortages could indeed be a very significant problem leading up to 2025, in two significant ways:
On one hand, we predict that the overall water demand in the country will increase by several billion gallons per day. We will attempt to solve this problem of total water supply by constructing additional 
de-salinization plants and reservoirs. We build these in the places that have the greatest predicted increase in their water demands.
The more significant problem however, as was the case in the drought of 2012-2013, is that even when there is enough water flowing in the United States as a whole, it might be the case that one city is flooding with water, while another is in drought.
The obvious solution here is a means of moving water across the country, and this can be accomplished by constructing a network of pipelines.

However, this isn't as simple as it may seem — it isn't enough to connect only a small number of cities with pipelines, because it's possible that droughts could occur in areas of the country not connected by those pipelines.
On the other hand, the cost of building pipelines in too many locations would be prohibitive.
Our paper solves this problem by finding a way to connect all of mainland USA with the minimum possible length of pipeline.
This solution is still quite expensive, but given the massive cost to the economy of droughts such as the 2012-2013 drought, we contend that it will is the most cost-effective solution to the United States' water problems.

@@

For the full details of our findings, please refer to our full paper,
attached below.

@@

Based on the average cost of de-salinization facilities noted above, it would cost \$79 billion to build enough de-salinization plants to meet this demand.

>>>>

In light of the 2012-2013 drought season, and the larger problem of growing demand for water across the nation, 
our department has conducted an
analysis of how best to satisfy the water needs of the United States.

The first part of our analysis is a projection of future water needs. 
We used data from previous years to predict the amount of additional
water that each county will need by 2025. Creating such a projection is critical, as it informs us
of what kinds of infrastructure needs to be developed, and how significant of a problem water shortages are likely to occur in the forseeable future.

Our projections suggest that water shortages could indeed be a very significant problem leading up to 2025, in two significant ways:
On one hand, we predict that the overall water demand in the country will increase by several billion gallons per day, confined to several areas of substantial increase. We will attempt to solve this problem of total water supply by constructing additional 
de-salinization plants and reservoirs. We build these in the places that have the greatest predicted increase in their water demands.
The more significant problem however, as was the case in the drought of 2012-2013, is that even when there is enough water flowing in the United States as a whole, it might be the case that one city is flooding with water, while another is in drought.
We advise constructing a means of moving water on a large scale across the country, and this can be accomplished by constructing a network of high-volume pipelines.

However, this isn't as simple as it may seem — it isn't enough to connect only a small number of cities with pipelines, because it's possible that droughts could occur in areas of the country not connected by those pipelines.
On the other hand, the cost of building pipelines in too many locations would be prohibitive.
Our paper solves this problem by finding a way to connect all of mainland USA with the minimum possible length of pipeline.
This solution is still quite expensive, at a projected cost of \$92 billion dollars, but given the massive cost to the economy of droughts such as the 2012-2013 drought, we contend that it will is the most cost-effective solution to the United States' water problems.

@@

For the full details of our findings, please refer to our paper,
attached below.

@@

Based on the average cost of de-salinization facilities noted above, it would cost \$79 billion to build enough de-salinization plants to meet this demand:
